Cartogram Mapping and Application to Cancer Data.

### 2019-06-20 review_article.Rmd
Find more sources of atlases using cartogram (contiguous and non contigous)

<!--
Current atlases utilising choropleth methods include Australia:

@@

@DACQ

@@

Keep neighbours by keeping borders intact.

From a computer graphics perspective it is a problem of 'map deformation' to account for the value assigned to each area. @ACA discuss their implementation of three methods for creating value - by - area cartograms. Defining cells, and manipulating the display according to statistical value of the cell. 
@ECGC present the problem of maintaining shape presevation in non-contiguous cartograms.

eg. state by population
Highlight the value of animating contigous to see changes over time, US can be recognisable but animation aides interpretation

@@

Importance of the statistic in this area being communicated was more important than keeping geography recognisable.

This helps to draw attention to large value areas, relies on reader being able to see all areas on a map, and know the difference between initial geography and new layout given by a cartogram.

@@

@@

>>>>

<!--
Current atlases utilising choropleth methods 
- include Australia:

@@

@@

<!-- Compress this to 2 sentence introduction about methods. Focus on which atlases have implemented this technique.--->
Cartograms keep spatial relationships of neighbours intact by keeping borders when adjusting sizes.
From a computer graphics perspective it is a problem of 'map deformation' to account for the value assigned to each area. @ACA discuss their implementation of three methods for creating value - by - area cartograms. @ECGC present the problem of maintaining shape presevation in non-contiguous cartograms.

The intention is to allow the map space to highlight the distribution of the variable. However drawing attention to large value areas and allowing reader to see all significant areas on a map, relies on them also knowing the difference between initial geography and new layout given by a cartogram.
Importance of the statistic in this area being communicated was more important than keeping geography recognisable.

eg. state by population

@@

@@

@CVBGSD presents bivariate maps, using size and colour for different variables.

@@

@ECGC ?? Highlight the value of animating contigous to see changes over time, US can be recognisable but animation aides interpretation
